Reduced growth due to belowground sink limitation is not fully explained by reduced photosynthesis

### 2017-02-15 manuscript/editor_response_tree_physiology.Rmd
final edits of tree phys manuscript.  ready to resumbit.

\
*Response*: We agree with the editor's comments that the effects of soil volume have not been properly accounted for in several places in the manuscript. Particularly in the discussion we have clarified the nature of the effect type, where soil volume effects were often been over-emphasized. We agree that the stats are strongly influenced by the Free seedling, but this is also representative of the observed effects of root restriction on *A*~sat~, TNC and leaf N across all containers throughout all measurement campaigns. We feel that addressing individual effects of specific volume treatments would overly complicate the paper and combining all soil volume treatment effects would not improve our interpretation of the results.

@@

\
*Response*: Editorial change made.  We have included more examples of C losses beyond respiration.  The rest of the paragraph is also adjusted to discuss "C loss" as a more general inclusive term.

@@

\
*Response*: The reviewer asked for C concentration data for the whole plant instead of assuming 50% for woody plant tissues.  We only have C and N data for leaves and roots.  We therefore use the 50% assumption to convert dry seedling biomass to final seedling C.

@@

\
*Response*: The editor makes several good points here. We have re-written the equation to better describe the way daily total leaf net C gain (*P*~day~) was calculated. We have also removed the statement "Leaf respiration is included in the calculation of *P*." and added a accurate description of how the area based respiration component was calculated at each 15 minute interval in the modelling of leaf net photosynthesis rates.

@@

\
*Response*: It is difficult to accurately compare spot measurements of *A*~sat~ at saturating light inside the gas exchange cuvette with modelled values of *A*~n~ that are estimated over continually fluctuating meteorological conditions over 120 days. With simple modelling exercise, using Licor conditions and measured photosynthetic parameters the estimated rates are slightly higher than observed rates of *A*~sat~. Importantly, this does not effect the overall patterns of decreased CUE in containerized seedlings.

@@

\
*Response*: We agree with each of the editors points here.  With comment #6 we have now clearly defined the "total net leaf C gain term".  As the editor points out there are several places where leaf *A*~n~ is discussed inappropriately, especially in the discussion.  Throughout the manuscript we have revised use of terms for C gain to accurately reflect either measured photosynthesis rates (*A*~sat~), leaf level rates of net photosynthesis (*A*~n~) or modelled cumulative total net leaf C gain (*P*~day~).

@@

\
*Response*: We agree with the editor here.  We have introduced a new term *A*~mass~ to represent *A*~max~ on a mass basis.  This should help easily distinguish between the two variables in the text and is now consistent with Figure 4.

@@

\
*Response*: This point was overlooked by the authors. This statement has been removed from the results section.

@@

\
*Response*: editorial change made.  Change *A*~n~ to *A*~sat~ (measured values)

@@

\
*Response*: We agree with the editor's comments. There is convincing evidence that nutrient uptake was negatively affected in this experiment but the mechanism is yet unidentified. Understanding the processes by which belowground sink manipulation manifests belowground will be important for future experiments using local soils. We hope that this data-set and experimental design can aid in future experiments to further investigate the mechanisms underpinning belowground sink limitation.

@@

\
*Response*: editorial change made.  Changed *A*~n~ to *A*~sat~ (measured values). As with comment #10, *A*~sat~ values are also added in Table 3 to show reductions in measured leaf level photosynthesis in containerized seedlings.

>>>>

\
*Response*: We agree with the editor's comments that the effects of soil volume have not been properly accounted for in several places in the manuscript. In the revision, we have clarified the nature of the effect type, where soil volume effects were often over-emphasized. We agree that the stats are strongly influenced by the Free seedling.  However, relationships with rooting volume that develop through time were missing because root restriction affected *A*~sat~, TNC and leaf N immediately for newly produced leaves across all containers and then throughout all measurement campaigns. We feel that addressing individual effects of specific volume treatments would overly complicate the paper and combining all soil volume treatment effects would not improve our interpretation of the results.

@@

\
*Response*: We have now included more examples of C losses beyond respiration. The rest of the paragraph is also adjusted to discuss "C loss" as a more general inclusive term.

@@

\
*Response*: The reviewer asked for C concentration data for the whole plant instead of assuming 50% for woody plant tissues.  We only have C and N data for leaves and roots. We therefore use the 50% assumption for wood to convert dry seedling biomass to final seedling C.

@@

\
*Response*: The editor makes several good points here. We have re-written the equation to better describe the way daily total leaf net C gain (*P*~day~) was calculated. We have also removed the statement "Leaf respiration is included in the calculation of *P*." and added a more accurate description of how the area based respiration component was calculated at each 15 minute interval in the modelling of leaf net photosynthesis rates. Most importantly, the methods used to calculate total carbon uptake were correct, only the description of the methods was unclear.

@@

\
*Response*: It is difficult to accurately compare spot measurements of *A*~sat~ at saturating light inside the gas exchange cuvette with modelled values of *A*~n~ that are estimated over continually fluctuating meteorological conditions over 120 days. With a simple modelling exercise, using Licor conditions and measured photosynthetic parameters the estimated rates are comparable, and only slightly higher than observed rates of *A*~sat~. Importantly, this does not effect the overall patterns of decreased CUE in containerized seedlings.

@@

\
*Response*: We agree with each of the editors points here.  With comment #6 we have now clearly defined the "total net leaf C gain term".  As the editor points out there are several places where leaf *A*~n~ was used inappropriately, especially in the discussion.  Throughout the manuscript we have revised use of terms for C gain to accurately reflect either measured photosynthesis rates at saturating light (*A*~sat~), leaf level rates of net photosynthesis at prevailing conditions (*A*~n~) or modelled total net leaf C gain (*P*~day~).

@@

\
*Response*: We agree with the editor here.  We have introduced a new term (*A*~mass~) to represent *A*~max~ on a mass basis.  This should help easily distinguish between the two variables in the text and is now consistent with Figure 4.

@@

\
*Response*: This statement has been removed from the results section.

@@

\
*Response*: editorial change made.  Change *A*~n~ to *A*~sat~ (measured values at saturating light)

@@

\
*Response*: We agree with the editor's comments. There is convincing evidence that nutrient uptake was negatively affected in this experiment but we lack any data on mineralization rate. Unfortunately we also did not measure available P, or any other detailed description of the nutrient cycle. Clearly such measurements were outside the scope of the study. We hope that this data set and experimental design can aid in future experiments to further investigate the mechanisms underpinning belowground sink limitation.

@@

\
*Response*: editorial change made.  Changed *A*~n~ to *A*~sat~ (measured values at saturating light). As with comment #10, *A*~sat~ values are also added in Table 3 to show reductions in measured leaf level photosynthesis in containerized seedlings.

### 2017-02-15 manuscript/manuscript_pve_editor.Rmd
final edits of tree phys manuscript.  ready to resumbit.

where *L* is modelled total plant leaf area (m^2^), $\sigma$ is a self-shading parameter and  *P*~day~ is the net daily C assimilation per unit leaf area (g C m^-2^).

>>>>

where *L* is total plant leaf area (m^2^), $\sigma$ is a self-shading parameter and *P*~day~ is the net daily C assimilation per unit leaf area, accounting for leaf respiratory losses (g C m^-2^).
